Convective dynamics with mixed temperature boundary conditions: \\ why thermal relaxation matters and how to accelerate it

### 2020-05-11 tex/mixedft_evolution_ms.tex
draft of revamp of 3D figure

\begin{table}[b!]
\vspace{-0.5cm}
\caption{ 
	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
	\ea{Note that the coefficient resolution of the evolved FT simulation and the TT-to-FT simulation are the same (nz, nx) = (1024, 2048).}
}
\vspace{-0.25cm}
\setlength{\tabcolsep}{12pt}
\label{table:pdf_values}
\begin{center}
\begin{tabular}{c c c c c c}
\hline																	
Quantity &	Case	&	$\mu$	&	$\sigma$	&	Skewness	&	Kurtosis \\
\hline
$T$				&	FT			&		$1.03 \times 10^{-2}$	&	$1.49 \times 10^{-3}$	&	0.656		&	27.0 \\
				&	TT-to-FT	&		$1.05 \times 10^{-2}$	&	$1.53 \times 10^{-3}$	&	0.729		&	26.8 \\
\hline
$\omega^2$		&	FT			&		$16.7$					&	$10.3$					&	96.2		&	$2.72 \times 10^4$ \\
				&	TT-to-FT	&		$11.7$					&	$10.6$					&	86.0		&	$1.63 \times 10^4$ \\
\hline
$wT$			&	FT			&		$4.50 \times 10^{-6}$	&	$4.87 \times 10^{-4}$	&	0.0133	&	$3.06$ \\
				&	TT-to-FT	&		$4.47 \times 10^{-6}$	&	$5.08 \times 10^{-4}$	&	0.0110	&	$3.06$ \\
\hline
$w$				&	FT			&		$3.62 \times 10^{-6}$	&	$4.70 \times 10^{-2}$	&	-0.0211	&	$3.00$ \\
				&	TT-to-FT	&		$4.22 \times 10^{-6}$	&	$4.82 \times 10^{-2}$	&	-0.0187	&	$3.02$ \\
\hline																	
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[b!]
\vspace{-0.5cm}
\caption{ 
	The first four moments, as defined in Eqn.~\ref{eqn:pdf_moments}, of each of the PDFs shown in Fig.~\ref{fig:rbc_restart_description} are displayed below.
	\ea{Note that the coefficient resolution of the evolved FT simulation and the TT-to-FT simulation are the same (nz, nx) = (1024, 2048).}
}
\vspace{-0.25cm}
\setlength{\tabcolsep}{12pt}
\label{table:pdf_values}
\begin{center}
\begin{tabular}{c c c c c c c}
\hline																	
Quantity 				&	BCs	& ICs	    &	$\mu$					&	$\sigma$				&	Skewness	&	Excess Kurtosis \\
\hline
$T/\Delta T$			&	TT	& Classic	&	$5.00 \times 10^{-1}$	&	$7.11 \times 10^{-2}$	&	$-1.53 \times 10^{-2}$	&	$1.71 \times 10^{1}$ \\
						&	FT	& Classic	&	$5.07 \times 10^{-1}$	&	$7.37 \times 10^{-2}$	&	$7.31 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
						&	FT	& TT-to-FT	&	$5.08 \times 10^{-1}$	&	$7.34 \times 10^{-2}$	&	$7.18 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
						&	FT	& Nu-based	&	$5.06 \times 10^{-1}$	&	$7.36 \times 10^{-2}$	&	$7.63 \times 10^{-1}$	&	$2.40 \times 10^{1}$ \\
\hline                                                                                                                      
$\omega^2/\Delta T$		&	TT	& Classic	&	$3.99 \times 10^{2}$	&	$4.73 \times 10^{2}$	&	$5.87 \times 10^{1}$	&	$6.68 \times 10^{3}$ \\
						&	FT	& Classic	&	$9.30 \times 10^{2}$	&	$4.79 \times 10^{2}$	&	$8.13 \times 10^{1}$	&	$1.76 \times 10^{4}$ \\
						&	FT	& TT-to-FT	&	$6.37 \times 10^{2}$	&	$5.02 \times 10^{2}$	&	$6.56 \times 10^{1}$	&	$8.69 \times 10^{3}$ \\
						&	FT	& Nu-based	&	$6.94 \times 10^{2}$	&	$4.84 \times 10^{2}$	&	$7.27 \times 10^{1}$	&	$1.20 \times 10^{4}$ \\
\hline                                                                                                                      
$wT/(\Delta T)^{3/2}$	&	TT	& Classic	&	$1.46 \times 10^{-3}$	&	$1.63 \times 10^{-1}$	&	$5.14 \times 10^{-2}$	&	$5.85  \times 10^{-2}$ \\
						&	FT	& Classic	&	$1.53 \times 10^{-3}$	&	$1.69 \times 10^{-1}$	&	$3.28 \times 10^{-2}$	&	$-8.19 \times 10^{-2}$ \\
						&	FT	& TT-to-FT	&	$1.51 \times 10^{-3}$	&	$1.67 \times 10^{-1}$	&	$3.63 \times 10^{-2}$	&	$1.29  \times 10^{-1}$ \\
						&	FT	& Nu-based	&	$1.50 \times 10^{-3}$	&	$1.70 \times 10^{-1}$	&	$4.37 \times 10^{-2}$	&	$1.95  \times 10^{-1}$ \\
\hline                                                                                                                    
$w/(\Delta T)^{1/2}$ 	&	TT	& Classic	&	$-3.11 \times 10^{-5}$	&	$3.25 \times 10^{-1}$	&	$1.64 \times 10^{-2}$	&	$-1.16 \times 10^{-2}$ \\
						&	FT	& Classic	&	$-3.80 \times 10^{-5}$	&	$3.33 \times 10^{-1}$	&	$1.75 \times 10^{-3}$	&	$-1.48 \times 10^{-1}$ \\
						&	FT	& TT-to-FT	&	$2.66  \times 10^{-5}$	&	$3.29 \times 10^{-1}$	&	$-1.21 \times 10^{-3}$	&	$7.89  \times 10^{-2}$ \\
						&	FT	& Nu-based	&	$2.41  \times 10^{-5}$	&	$3.35 \times 10^{-1}$	&	$1.08 \times 10^{-2}$	&	$1.37  \times 10^{-1}$ \\
\hline																	
\end{tabular}
\end{center}
\end{table}
